---
title: "Jobs"
output:
  pdf_document: default
  html_document: default
---

```{r libraries, message=FALSE, warning=FALSE}

# Load tidyverse, which includes the packages: ggplot2 (a package for plots) and
# dplyr (a package for wrangling data)
library(tidyverse)
# load broom which is a package that prints tables neatly 
# we'll use it to print regression tables
library(broom)
# load ggrepel, which is a package to print text on a graph neatly
# we'll use it later when making scatterplots
library(ggrepel)

# Load data: the `../` bit means "go to the folder one level above the folder in which this script is saved"
load("../data/jobs.RData")

```

What's the unit of analysis?

## 1.1 How years of experience predicts the wage rate 

Let's make a scatterplot with the wage rate on the vertical and years of experience on the horizontal axes.

```{r wage-experience-scatter}
ggplot(jobs, aes(x = years_of_experience, y = median_wage_rate)) +
  geom_point(alpha = 0.3, size = 2) +
  
  # Linear fit
  geom_smooth(
    aes(colour = "Linear", linetype = "Linear"),
    method = "lm", 
    formula = y ~ x, 
    se = FALSE
  ) +
  
  # Quadratic fit
  geom_smooth(
    aes(colour = "Quadratic", linetype = "Quadratic"),
    method = "lm", 
    formula = y ~ x + I(x^2), 
    se = FALSE
  ) +
 
  # Cubic fit
  geom_smooth(
    aes(colour = "Cubic", linetype = "Cubic"),
    method = "lm",
    formula = y ~ x + I(x^2) + I(x^3),
    se = FALSE
  ) + 
  
  scale_colour_manual(
    name = "Model",
    values = c(
      "Linear" = "blue",
      "Quadratic" = "black",
      "Cubic" = "red"
    )
  ) +
  
  scale_linetype_manual(
    name = "Model",
    values = c(
      "Linear" = "dotted",
      "Quadratic" = "solid",
      "Cubic" = "dashed"
    )
  ) +
  
  labs(
    title = "Wage Rate vs Years of Experience",
    x = "Average Years of Experience",
    y = "Median Wage Rate"
  ) +
  theme_minimal()
```

Which of these plots would you choose to describe the relationship between wages and years of experience --- linear, quadratic or cubic? When you choose, consider how you would like to strike the balance between accuracy and complexity of the model --- especially when you describe what the model predicts (the shape of the fit) to a person who doesn't understand data analysis very much. Hints: Consider how you think wage rate grows with years of experiences, general trends (up, down), peaks, plateau.

I sometimes find it helpful to label a few dots to get a general "feel" for what the data is saying. 

```{r wage-experience-labelled}

ggplot(jobs, aes(x = years_of_experience, y = median_wage_rate)) +
  
  # Scatterplot
  geom_point(alpha = 0.3, size = 2) +
  
  # Labels for selected occupations
  geom_text_repel(
    data = subset(
      jobs,
      years_of_experience > 45 |
      median_wage_rate > 60 |
      years_of_experience < 15
    ),
    aes(label = soc_description),
    size = 3,
    max.overlaps = Inf
  ) +
  
   # Linear fit
  geom_smooth(
    aes(colour = "Linear", linetype = "Linear"),
    method = "lm", 
    formula = y ~ x, 
    se = FALSE
  ) +
  
  # Quadratic fit
  geom_smooth(
    aes(colour = "Quadratic", linetype = "Quadratic"),
    method = "lm", 
    formula = y ~ x + I(x^2), 
    se = FALSE
  ) +
 
  # Cubic fit
  geom_smooth(
    aes(colour = "Cubic", linetype = "Cubic"),
    method = "lm",
    formula = y ~ x + I(x^2) + I(x^3),
    se = FALSE
  ) + 
  
  scale_colour_manual(
    name = "Model",
    values = c(
      "Linear" = "blue",
      "Quadratic" = "black",
      "Cubic" = "red"
    )
  ) +
  
  scale_linetype_manual(
    name = "Model",
    values = c(
      "Linear" = "dotted",
      "Quadratic" = "solid",
      "Cubic" = "dashed"
    )
  ) +
  
  labs(
    title = "Wage Rate vs Years of Experience",
    x = "Average Years of Experience",
    y = "Median Wage Rate"
  ) +
  
  theme_minimal()
```

## 1.2 Visualizing dummy variables as regressors


Before we visualize dummy variables as regressors, let's make a simple plot comparing wage rate to years of education.

```{r wage-education-scatter}
ggplot(jobs, aes(x = avg_years_of_education, y = median_wage_rate)) +
  geom_point() +
  labs(
    title = "Wage Rate vs Education",
    x = "Average Years of Education",
    y = "Median Wage Rate"
  ) +
  theme_minimal()
```

There are 3 income groups for a given occupation --- high, medium and low. Each of the income groups are given by a dummy variable. Let's see some examples.

```{r example-income-groups-display}

jobs %>%
  select(
    soc_description,
    median_wage_rate,
    high_income_occ,
    medium_income_occ,
    low_income_occ
  ) %>%
  group_by(high_income_occ, medium_income_occ, low_income_occ) %>%
  slice_head(n = 3) %>%
  ungroup()

```


Now repeat the wage-education scatterplot, colouring the points differently by the income group. 


```{r wage-educ-category-scatterplot}
ggplot(jobs, aes(x = avg_years_of_education,
                 y = median_wage_rate)) +
  geom_point(data = subset(jobs, low_income_occ == 1),
             aes(colour = "Low")) +
  geom_point(data = subset(jobs, medium_income_occ == 1),
             aes(colour = "Medium")) +
  geom_point(data = subset(jobs, high_income_occ == 1),
             aes(colour = "High")) +
  labs(
    title = "Wage Rate vs Education by Income Level",
    x = "Average Years of Education",
    y = "Median Wage Rate",
    colour = "Income Level"
  ) +
  theme_minimal()
```


Fit a line through all the points. 


```{r wage-educ-category-single-fit}
ggplot(jobs, aes(x = avg_years_of_education,
                 y = median_wage_rate)) +
  
  # Points coloured by income group
  geom_point(data = subset(jobs, low_income_occ == 1),
             aes(colour = "Low")) +
  geom_point(data = subset(jobs, medium_income_occ == 1),
             aes(colour = "Medium")) +
  geom_point(data = subset(jobs, high_income_occ == 1),
             aes(colour = "High")) +
  
  # One fitted line through all observations
  geom_smooth(
    method = "lm",
    formula = y ~ x,
    se = FALSE,
    colour = "black"
  ) +
  
  labs(
    title = "Wage Rate vs Education by Income Level",
    x = "Average Years of Education",
    y = "Median Wage Rate",
    colour = "Income Level"
  ) +
  
  theme_minimal()
```

This model assumes all occupations have on average, the same increase of wages predicted by an additional year of education.

Now fit 3 lines through the 3 income groups, with each line having the same slope.

To do so, start with the regression below. Why did we leave out the low income occupation group?

```{r wage-educ-income-reg}
# Regression with common slope and different intercepts
wage_educ_income_reg <- lm(
  median_wage_rate ~ avg_years_of_education +
    medium_income_occ + high_income_occ,
  data = jobs
)

tidy(wage_educ_income_reg)
```


Extract the slopes

```{r wage-educ-and-income-slopes}
# Store coefficients
educ_slope <- coef(wage_educ_income_reg)["avg_years_of_education"]

low_intercept <- coef(wage_educ_income_reg)["(Intercept)"]

medium_intercept <- coef(wage_educ_income_reg)["(Intercept)"] +
  coef(wage_educ_income_reg)["medium_income_occ"]

high_intercept <- coef(wage_educ_income_reg)["(Intercept)"] +
  coef(wage_educ_income_reg)["high_income_occ"]
```


Plot scatter with a separate line fit for each income group


```{r wage-educ-income-scatter-1}
# Plot
ggplot(jobs, aes(x = avg_years_of_education,
                 y = median_wage_rate)) +
  
  # Scatter points
  geom_point(data = subset(jobs, low_income_occ == 1),
             aes(colour = "Low")) +
  geom_point(data = subset(jobs, medium_income_occ == 1),
             aes(colour = "Medium")) +
  geom_point(data = subset(jobs, high_income_occ == 1),
             aes(colour = "High")) +
  
  # Parallel fitted lines
  geom_abline(aes(intercept = low_intercept,
                  slope = educ_slope,
                  colour = "Low"),
              linewidth = 1) +
  
  geom_abline(aes(intercept = medium_intercept,
                  slope = educ_slope,
                  colour = "Medium"),
              linewidth = 1) +
  
  geom_abline(aes(intercept = high_intercept,
                  slope = educ_slope,
                  colour = "High"),
              linewidth = 1) +
  
  labs(
    title = "Wage Rate vs Education by Income Level",
    x = "Average Years of Education",
    y = "Median Wage Rate",
    colour = "Income Level"
  ) +
  theme_minimal()
```

This model predicts that high income earners wages are greater than middle income earners, which is greater than low income earners, on average.
But given their income group, an additional year of education predicts the same increase in wages, on average.

Which line fit feels more honest? The one with 3 lines, or with one line? Why?


Now we fit 3 lines, but allow the slopes to vary for each income group.


```{r wage-educ-by-income-scatter}

ggplot(jobs, aes(x = avg_years_of_education,
                 y = median_wage_rate)) +
  
  # Low income
  geom_point(data = subset(jobs, low_income_occ == 1),
             aes(colour = "Low")) +
  geom_smooth(data = subset(jobs, low_income_occ == 1),
              aes(colour = "Low"),
              method = "lm",
              formula = y ~ x,
              se = FALSE) +
  
  # Medium income
  geom_point(data = subset(jobs, medium_income_occ == 1),
             aes(colour = "Medium")) +
  geom_smooth(data = subset(jobs, medium_income_occ == 1),
              aes(colour = "Medium"),
              method = "lm",
              formula = y ~ x,
              se = FALSE) +
  
  # High income
  geom_point(data = subset(jobs, high_income_occ == 1),
             aes(colour = "High")) +
  geom_smooth(data = subset(jobs, high_income_occ == 1),
              aes(colour = "High"),
              method = "lm",
              formula = y ~ x,
              se = FALSE) +
  
  labs(
    title = "Wage Rate vs Education by Income Level",
    x = "Average Years of Education",
    y = "Median Wage Rate",
    colour = "Income Level"
  ) +
  theme_minimal()

```

This model predicts that each additional year of education gives on average, a larger rise of wages for high income earners, compared to medium income earners; and similarly, a larger rise in wages for medium income earners compared to low income earners.

Write the model for each plot. Do you see that each model excludes predictors that the next model includes?

Which of these 3 models would you pick and why?

Approximately (no need to calculate this), what's the average years of education and wage rate for each income group? Hint: read the horizontal and vertical axis value for the midpoint of each line.


## 1.3: Visualizing multiple linear regressions


Now we see what controlling for a variable or adding extra regressors/predictors means, and we take this procedure in steps.


### Regressions as estimators of averages

First plot the wage rate on vertical axis, and income groups on horizontal axis. Then calculate the averages.

```{r wage-income-scatter}

ggplot(
  jobs,
  aes(
    x = factor(
      case_when(
        low_income_occ == 1 ~ "Low",
        medium_income_occ == 1 ~ "Medium",
        high_income_occ == 1 ~ "High"
      ),
      levels = c("Low", "Medium", "High")
    ),
    y = median_wage_rate
  )
) +
  geom_point() +
  labs(
    title = "Wage Rate by Income Group",
    x = "Income Group",
    y = "Median Wage Rate"
  ) +
  theme_minimal()
```
```{r wage-income-avgs}
jobs %>%
  summarise(
    low = mean(median_wage_rate[low_income_occ == 1]),
    medium = mean(median_wage_rate[medium_income_occ == 1]),
    high = mean(median_wage_rate[high_income_occ == 1])
  )
```


Now run the following regression.


```{r wage-income-reg}
wage_income_reg <- lm(
  median_wage_rate ~ medium_income_occ + high_income_occ,
  data = jobs
)
tidy(wage_income_reg)
```


What do you conclude about the coefficients of the dummy variables in this regression? What do they help you calculate? (Hint: The intercept is the same as? Can I exactly get the averages for the medium and high income groups using the coefficients of the dummy variables?)


Similarly, for education.


```{r educ-income-scatter}

ggplot(
  jobs,
  aes(
    x = factor(
      case_when(
        low_income_occ == 1 ~ "Low",
        medium_income_occ == 1 ~ "Medium",
        high_income_occ == 1 ~ "High"
      ),
      levels = c("Low", "Medium", "High")
    ),
    y = avg_years_of_education
  )
) +
  geom_point() +
  labs(
    title = "Years of Education by Income Group",
    x = "Income Group",
    y = "Years of Education"
  ) +
  theme_minimal()
```
```{r educ-income-avgs}
jobs %>%
  summarise(
    low = mean(avg_years_of_education[low_income_occ == 1]),
    medium = mean(avg_years_of_education[medium_income_occ == 1]),
    high = mean(avg_years_of_education[high_income_occ == 1])
  )
```

```{r educ-income-reg}
educ_income_reg <- lm(
  avg_years_of_education ~ medium_income_occ + high_income_occ,
  data = jobs
)
tidy(educ_income_reg)
```


Do you see the same thing?

Did R give you the same numbers as you guessed in the previous section?

Now let's focus on the low income group, with the average wage in this group plotted in red. 


```{r wage-income-scatter-lowinc}

ggplot(
  filter(jobs, low_income_occ == 1),
  aes(
    x = "Low",
    y = median_wage_rate
  )
) +
  geom_point() +
  
  # Average wage
  geom_hline(
    yintercept = mean(
      jobs$median_wage_rate[jobs$low_income_occ == 1],
      na.rm = TRUE
    ),
    colour = "red",
    linewidth = 1
  ) +
  
  scale_y_continuous(
    breaks = seq(0, 40, by = 5)
  ) +
  
  labs(
    title = "Wage Rate for the Low Income Group",
    x = "Income Group",
    y = "Median Wage Rate"
  ) +
  theme_minimal()

```


How do you identify the residual in this plot?


In the picture above, the residual gives the deviation of each job's wage rate from the average wage rate of the ____ income group.


```{r educ-income-scatter-lowinc}

ggplot(
  filter(jobs, low_income_occ == 1),
  aes(
    x = "Low",
    y = avg_years_of_education
  )
) +
  geom_point() +
  
  # Average wage
  geom_hline(
    yintercept = mean(
      jobs$avg_years_of_education[jobs$low_income_occ == 1],
      na.rm = TRUE
    ),
    colour = "red",
    linewidth = 1
  ) +
  
  scale_y_continuous(
    breaks = seq(0, 40, by = 5)
  ) +
  
  labs(
    title = "Years of Education for the Low Income Group",
    x = "Income Group",
    y = "Average Years of Education"
  ) +
  theme_minimal()

```


In the picture above, the residual gives the deviation of each job's years of education from the average years of education of the ____ income group.


Back to our old plot but adding fitted values.


```{r wage-income-scatter-w-fittedavg}
ggplot(
  jobs,
  aes(
    x = factor(
      case_when(
        low_income_occ == 1 ~ "Low",
        medium_income_occ == 1 ~ "Medium",
        high_income_occ == 1 ~ "High"
      ),
      levels = c("Low", "Medium", "High")
    ),
    y = median_wage_rate
  )
) +
  geom_point() +
  
  # Fitted average for each income group
  stat_summary(
    fun = mean,
    geom = "crossbar",
    width = 0.5,
    colour = "red",
    linewidth = 1
  ) +
  
  labs(
    title = "Wage Rate by Income Group",
    x = "Income Group",
    y = "Median Wage Rate"
  ) +
  theme_minimal()
```


The residuals in this plot describes the deviation of each job's wage rate from the average wage rate for each ____ group
OR
The residuals give the wage dispersion, in each _____ group.
OR 
The residuals give the wage dispersion, within each _____ group.


```{r educ-income-scatter-w-fittedavg}
ggplot(
  jobs,
  aes(
    x = factor(
      case_when(
        low_income_occ == 1 ~ "Low",
        medium_income_occ == 1 ~ "Medium",
        high_income_occ == 1 ~ "High"
      ),
      levels = c("Low", "Medium", "High")
    ),
    y = avg_years_of_education
  )
) +
  geom_point() +
  
  # Fitted average for each income group
  stat_summary(
    fun = mean,
    geom = "crossbar",
    width = 0.5,
    colour = "red",
    linewidth = 1
  ) +
  
  labs(
    title = "Years of Education by Income Group",
    x = "Income Group",
    y = "Years of Education"
  ) +
  theme_minimal()
```

The residuals in this plot describes the deviation of each job's average years of education from the average years of education for each ____ group
OR
The residuals give the dispersion of average years of education, within each _____ group.


### Multiple linear regression as residual dispersion after controls

Suppose we have the regression, 

$$Wage_i = \beta_0 + \beta_1 Education_i + \beta_2MediumIncome_i + \beta_3HighIncome_i + \varepsilon_i.$$

How do we interpret $\beta_1$?

To do so, let's first find the coefficient estimate $\hat{\beta_1}$.


```{r print-coef-wage-educ-inc-reg}

tidy(wage_educ_income_reg) %>%
  filter(term == "avg_years_of_education") %>%
  select(estimate, std.error)

```


And let's remind ourselves that this is the same slope as in the 3 lines below:

```{r wage-educ-income-scatter-2}
# Plot
ggplot(jobs, aes(x = avg_years_of_education,
                 y = median_wage_rate)) +
  
  # Scatter points
  geom_point(data = subset(jobs, low_income_occ == 1),
             aes(colour = "Low")) +
  geom_point(data = subset(jobs, medium_income_occ == 1),
             aes(colour = "Medium")) +
  geom_point(data = subset(jobs, high_income_occ == 1),
             aes(colour = "High")) +
  
  # Parallel fitted lines
  geom_abline(aes(intercept = low_intercept,
                  slope = educ_slope,
                  colour = "Low"),
              linewidth = 1) +
  
  geom_abline(aes(intercept = medium_intercept,
                  slope = educ_slope,
                  colour = "Medium"),
              linewidth = 1) +
  
  geom_abline(aes(intercept = high_intercept,
                  slope = educ_slope,
                  colour = "High"),
              linewidth = 1) +
  
  labs(
    title = "Wage Rate vs Education by Income Level",
    x = "Average Years of Education",
    y = "Median Wage Rate",
    colour = "Income Level"
  ) +
  theme_minimal()
```


Let's plot the lines corresponding to the means of the high, medium and low income groups' wage and education.


```{r wage-educ-inclines-scatter}
# Group means
low_mean_wage <- mean(
  jobs$median_wage_rate[jobs$low_income_occ == 1],
  na.rm = TRUE
)
low_mean_educ <- mean(
  jobs$avg_years_of_education[jobs$low_income_occ == 1],
  na.rm = TRUE
)

medium_mean_wage <- mean(
  jobs$median_wage_rate[jobs$medium_income_occ == 1],
  na.rm = TRUE
)
medium_mean_educ <- mean(
  jobs$avg_years_of_education[jobs$medium_income_occ == 1],
  na.rm = TRUE
)

high_mean_wage <- mean(
  jobs$median_wage_rate[jobs$high_income_occ == 1],
  na.rm = TRUE
)
high_mean_educ <- mean(
  jobs$avg_years_of_education[jobs$high_income_occ == 1],
  na.rm = TRUE
)


# Plot
ggplot(jobs, aes(x = avg_years_of_education,
                 y = median_wage_rate)) +
  
  # Scatter points
  geom_point(
    data = subset(jobs, low_income_occ == 1),
    aes(colour = "Low")
  ) +
  geom_point(
    data = subset(jobs, medium_income_occ == 1),
    aes(colour = "Medium")
  ) +
  geom_point(
    data = subset(jobs, high_income_occ == 1),
    aes(colour = "High")
  ) +
  
  # Mean education: vertical lines
  geom_vline(
    aes(xintercept = low_mean_educ, colour = "Low"),
    linetype = "dashed",
    linewidth = 1,
    alpha = 0.4
  ) +
  geom_vline(
    aes(xintercept = medium_mean_educ, colour = "Medium"),
    linetype = "dashed",
    linewidth = 1,
    alpha = 0.4
  ) +
  geom_vline(
    aes(xintercept = high_mean_educ, colour = "High"),
    linetype = "dashed",
    linewidth = 1,
    alpha = 0.4
  ) +
  
  # Mean wage: horizontal lines
  geom_hline(
    aes(yintercept = low_mean_wage, colour = "Low"),
    linetype = "dashed",
    linewidth = 1,
    alpha = 0.4
  ) +
  geom_hline(
    aes(yintercept = medium_mean_wage, colour = "Medium"),
    linetype = "dashed",
    linewidth = 1,
    alpha = 0.4
  ) +
  geom_hline(
    aes(yintercept = high_mean_wage, colour = "High"),
    linetype = "dashed",
    linewidth = 1,
    alpha = 0.4
  ) +
  
  labs(
    title = "Wage Rate vs Education by Income Level",
    x = "Average Years of Education",
    y = "Median Wage Rate",
    colour = "Income Level"
  ) +
  theme_minimal()
```


We will de-mean the wage and education variables as in a simple linear regression. But this time we will demean by its means within the same income group.


```{r residual-regressions}

# (1) Regress wage rate on the three income-level dummies
reg_wage <- lm(
  median_wage_rate ~ low_income_occ + medium_income_occ + high_income_occ - 1,
  data = jobs
)

# (2) Regress education on the three income-level dummies
reg_education <- lm(
  avg_years_of_education ~ low_income_occ + medium_income_occ + high_income_occ - 1,
  data = jobs
)

# Store residuals as new columns
jobs$wage_residual <- residuals(reg_wage)
jobs$education_residual <- residuals(reg_education)


# Plot residualised wage against residualised education
ggplot(jobs, aes(x = education_residual,
                 y = wage_residual)) +
  
  geom_point(data = subset(jobs, low_income_occ == 1),
             aes(colour = "Low")) +
  
  geom_point(data = subset(jobs, medium_income_occ == 1),
             aes(colour = "Medium")) +
  
  geom_point(data = subset(jobs, high_income_occ == 1),
             aes(colour = "High")) +
  
  labs(
    title = "Wage Rate vs Education",
    subtitle = "Controlling for Income Level",
    x = "Average Years of Education (after accounting for income level)",
    y = "Median Wage Rate (after accounting for income level)",
    colour = "Income Level"
  ) +
  
  theme_minimal()

```

What's the intercept of this line?

Let's find the slope of this line, and compare it to a coefficient from the old regression for 3 lines with the same slope.


```{r wage-educ-residualized}
wage_educ_residualized_reg <- lm(
  wage_residual ~ education_residual,
  data = jobs
)
tidy(wage_educ_residualized_reg)
```


Is the coefficient and standard error different?

Now let's add the 95% confidence intervals for the lines. 

```{r wage-educ-resid-with-ci-scatter}
# Plot residualised wage against residualised education
ggplot(jobs, aes(x = education_residual,
                 y = wage_residual)) +
  
  geom_point(data = subset(jobs, low_income_occ == 1),
             aes(colour = "Low")) +
  
  geom_point(data = subset(jobs, medium_income_occ == 1),
             aes(colour = "Medium")) +
  
  geom_point(data = subset(jobs, high_income_occ == 1),
             aes(colour = "High")) +
  
  # Linear fit with 95% confidence interval
  geom_smooth(
    method = "lm",
    formula = y ~ x,
    se = TRUE,
    colour = "black",
    alpha = 0.6
  ) +
  
  scale_x_continuous(
    breaks = scales::breaks_pretty(n = 6)
  ) +
  
  scale_y_continuous(
    breaks = scales::breaks_pretty(n = 6)
  ) +
  
  labs(
    title = "Wage Rate vs Education",
    subtitle = "Controlling for Income Level",
    x = "Average Years of Education (after accounting for income level)",
    y = "Median Wage Rate (after accounting for income level)",
    colour = "Income Level"
  ) +
  
  theme_minimal()
```

We regressed the within income group wages against the within income group years of education to get the same slope as $\beta_1$ from 

$$Wage_i = \beta_0 + \beta_1 Education_i + \beta_2MediumIncome_i + \beta_3HighIncome_i + \varepsilon_i.$$

Therefore, $\hat{\beta_1}$ can be interpreted as: how within an income group, an extra year of education in any job is associated with an increase in wage per hour.
OR
For a given an income group, $\hat{\beta_1}$ gives the average increase in wage, for an increase in a year of education in any job.
OR
Accounting for broad differences between high, medium and low income occupations, $\hat{\beta_1}$ gives the average increase in wage, for an increase in a year of education in any job.

Seeing this graph, which model would you pick?

## 1.4: Visualizing the many-predictor problem

We follow the same procedure as earlier to add many regressors, while focusing on the wage-education relationship.

```{r residualise-with-controls}

reg_wage_controls <- lm(
  median_wage_rate ~
    high_income_occ +
    medium_income_occ +
    low_income_occ +
    number_of_transferable_skills +
    share_of_skills_at_level_5_proficiency +
    share_of_skills_at_level_4_proficiency +
    share_of_skills_at_level_3_proficiency +
    share_of_skills_at_level_2_proficiency +
    share_of_skills_at_level_1_proficiency +
    weighted_skill_score +
    managers_directors_senior_officials +
    professional_occupations +
    associate_professional_occupations +
    administrative_secretarial_occupations +
    skilled_trades_occupations +
    caring_leisure_other_service_occupations +
    sales_customer_service_occupations +
    process_plant_machine_operatives +
    elementary_occupations +
    years_of_experience +
    I(years_of_experience^2) - 1,
  data = jobs
)

# Store wage residuals
jobs$wage_residual_controls <- residuals(reg_wage_controls)
```

```{r residualise-education-with-controls}

reg_education_controls <- lm(
  avg_years_of_education ~
    high_income_occ +
    medium_income_occ +
    low_income_occ +
    number_of_transferable_skills +
    share_of_skills_at_level_5_proficiency +
    share_of_skills_at_level_4_proficiency +
    share_of_skills_at_level_3_proficiency +
    share_of_skills_at_level_2_proficiency +
    share_of_skills_at_level_1_proficiency +
    weighted_skill_score +
    managers_directors_senior_officials +
    professional_occupations +
    associate_professional_occupations +
    administrative_secretarial_occupations +
    skilled_trades_occupations +
    caring_leisure_other_service_occupations +
    sales_customer_service_occupations +
    process_plant_machine_operatives +
    elementary_occupations +
    years_of_experience +
    I(years_of_experience^2) - 1,
  data = jobs
)

# Store education residuals
jobs$education_residual_controls <- residuals(reg_education_controls)
```

```{r residual-plot-with-controls}

ggplot(jobs, aes(x = education_residual_controls,
                 y = wage_residual_controls)) +
  
  geom_point(data = subset(jobs, low_income_occ == 1),
             aes(colour = "Low")) +
  
  geom_point(data = subset(jobs, medium_income_occ == 1),
             aes(colour = "Medium")) +
  
  geom_point(data = subset(jobs, high_income_occ == 1),
             aes(colour = "High")) +
  
  scale_x_continuous(
    breaks = scales::breaks_pretty(n = 6)
  ) +
  
  scale_y_continuous(
    breaks = scales::breaks_pretty(n = 6)
  ) +
  
  labs(
    title = "Wage Rate vs Education",
    subtitle = "Controlling for skills, occupation and experience",
    x = "Average Years of Education (after controls)",
    y = "Median Wage Rate",
    colour = "Income Level"
  ) +
  
  theme_minimal()
```

Compare the range of values taken by the data on the vertical and horizontal axes. 

If you were to add more predictors, what would happen to the scatterplot eventually?

Let's test this by adding the best predictor of an occupation as a control --- a dummy for each occupation.


```{r soc-code-residualisation}

# (1) Residualise wage rate using SOC-code dummies
reg_wage_soc <- lm(
  median_wage_rate ~ factor(soc_code),
  data = jobs
)

# (2) Residualise education using SOC-code dummies
reg_education_soc <- lm(
  avg_years_of_education ~ factor(soc_code),
  data = jobs
)

# Store residuals
jobs$wage_residual_soc <- residuals(reg_wage_soc)
jobs$education_residual_soc <- residuals(reg_education_soc)


ggplot(jobs, aes(x = education_residual_soc,
                 y = wage_residual_soc)) +
  
  geom_point(data = subset(jobs, low_income_occ == 1),
             aes(colour = "Low")) +
  
  geom_point(data = subset(jobs, medium_income_occ == 1),
             aes(colour = "Medium")) +
  
  geom_point(data = subset(jobs, high_income_occ == 1),
             aes(colour = "High")) +
  
  labs(
    title = "Residualised Wage Rate vs Residualised Education",
    subtitle = "Controlling for SOC Code",
    x = "Residualised Average Years of Education",
    y = "Residualised Median Wage Rate",
    colour = "Income Level"
  ) +
  theme_minimal()

```
